
```{r, echo=FALSE, message = FALSE, warning = FALSE,,include=FALSE}
# TODO: caching the results
# ------------------------------------------- #
# CHANGE PARAMETERS HERE !
#setwd("C:/Users/Madhu/Documents/Availability")
#path_data <- paste(getwd(), 
 #                  "/CW 31", 
  #                 sep = "")
days <- as.Date(c("2016-09-19","2016-09-25"))

start_date<-strptime(days[1],format="%Y-%m-%d",tz="UTC")
last_date<-strptime(days[2]+1,format="%Y-%m-%d",tz="UTC")
# list of cities:
#   "Berlin", "London"
#city <-"London"

# list of clusters: 
#   "Nord Westen" "West", "Zentral", "North East",  "West (new)",  "Soho", "South", "Victoria", "City", "Southeast", "Camden" ,"Central"
#cluster <- "Central"


# ------------------------------------------- #
# Load the data
set.seed(1)
library(rmongodb)
source("make_customerbydate.R")
source("make_idletime.R")
source("make_geolocations.R")
source("load_data.R")
#load("df_all.dat")
#source("plot_functions.R")
# ###############
# #to be used only in standalone
# days <- c("2016-07-18","2016-07-24")
# city <-"Berlin"
# cluster<-"Nord Westen"

#city <-"London"
#clusters<-c("North East",  "West (new)",  "Soho", "South", "Victoria", "City", "Southeast", "Camden" ,"ALL")
#cluster<- "ALL"
# ##################
# filter on the relevant city and/or district
df_filtered <- df_all[df_all$City %in% city, ]
df_filtered[df_filtered$Cluster=="Nord Westen","Cluster"]<-"EBERTY-ZENTRAL"
df_filtered[df_filtered$Cluster=="Zentral","Cluster"]<-"EBERTY-ZENTRAL"
df_filtered[as.Date(df_filtered$Time.DO,format = "%m/%d/%y")<as.Date("2016-09-16") 
                    & (df_filtered$Cluster=="EBERTY-ZENTRAL"),"Cluster"]<-"Zentrallager"
if(cluster!="ALL"){
df_filtered <- df_filtered[df_filtered$Cluster %in% cluster, ]
}

```


## `r cluster`

#### Orders collected between the `r days[1]` and `r days[2]` in cluster `r cluster`

- Density Estimation: a method to evaluate the orders
- Shrink the clusters
- Analysis of the relevant customers

```{r,  echo=FALSE, message = FALSE, warning = FALSE,fig.width = 8, fig.height = 8 }


# plot the earning map
# plot_earning(df_filtered)
#plot_earning_lf(df_filtered)
    df_map <- mutate(df_filtered, 
                 basket = cut(Earning, 
                              breaks = c(1,20, 30, 40, 60, 1000), 
                              labels = c("0:20", "21:30", "31:40", "41:60", "61:1000")))
library(ggmap)

whichmap <- get_map(location=c(mean(df_map$Long),mean(df_map$Lat)), zoom = 12,color="bw")
Mapthewhichmap <- ggmap(whichmap, extent = "panel", legend = "bottomright")
Mapthewhichmap +geom_point(aes(x = Long, y = Lat, colour = basket),size=5,data = df_map)+scale_color_discrete(name = "Basket of order in Euro")

```


### Density estimation

#### Orders on the peripherie of the clusters are expensive

Below is represented the density estimation of orders in the cluster `r cluster`. 
Each line circles a fraction of the orders in the cluster (iso = 60% means 60% of the orders are located inside the contour).

```{r, echo=FALSE, message = FALSE, warning = FALSE,fig.width = 8, fig.height = 8}

# plot the density map
# plot_density_map(df_filtered)
# TODO : select ISO with "seq(95, 50, -5)"
#plot_density_map_lf(df_filtered)
Mapthewhichmap+geom_density2d(aes(x = Long, y = Lat,colour = ..level..),size=2,data = df_map, contour =TRUE,show.legend = FALSE) + geom_point(aes(x = Long, y = Lat),size=1,data = df_map)
#+scale_fill_gradient(low = "blue", high = "red")


```


### Statistics on the interactions
  
Here are some statistics on **all orders in the cluster**, to assess if there is a particular pattern:  
```{r, echo=FALSE}
df_filtered$Day <- as.factor(df_filtered$Day)
df_filtered$Weekday <- factor(df_filtered$Weekday, 
                             levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
df_filtered$Type <- as.factor(df_filtered$Type)
df_filtered$From <- factor(df_filtered$From, 
                       levels = c("7:00", "8:00", "9:00", "10:00", "11:00", "12:00", "13:00", 
                                  "14:00", "15:00", "16:00", "17:00", "18:00", "19:00", 
                                  "20:00", "21:00", "22:00", "23:00"))
# customers
nb_cust_all <- length(unique(df_filtered[,"CustomerID"]))
# travel time
a_from_all <- round(mean(df_filtered$from_time)/60, 1)
a_to_all <- round(mean(df_filtered$to_time)/60, 1)
a_tot_all <- a_from_all + a_to_all
# aov
aov_all <- round(mean(df_filtered$Earning), 2)
# timeslots
x <- as.character(df_filtered$From)
x <- as.numeric(unlist(strsplit(x, ":")))
x <- x[x < 25 & x > 0]

frac_timeslots <- rep(0, 3)
frac_timeslots[1] <- length(x[x < 10])/length(x)*100
frac_timeslots[3] <- length(x[x >= 18])/length(x)*100
frac_timeslots[2] <- 100 - frac_timeslots[3] - frac_timeslots[1]
frac_timeslots <- round(frac_timeslots, 1)

# weekdays
frac_weekday <- round(sapply(levels(df_filtered$Weekday), 
                             FUN = function(x, y){sum(y$Weekday == x)/nrow(y)*100},
                             y = df_filtered), 1)


# knitr::kable(summary(df_filtered[, c("Day", "Weekday", 
#                                  "From", "Type", "Earning", 
#                                  "Status", "to_time", "from_time")]), 
#              caption = "Summary Table")
summary(df_filtered[, c("Day", "Weekday", "From", "Type", "Earning",  "to_time", "from_time")])

```



Here is presented the repartition of the interactions according to **weekdays** and **hours**:  
```{r, echo=FALSE}
# round(table(data.frame(Time = cut(x, breaks = c(0, 10, 17, 24)), 
#                        Weekday = df_filtered$Weekday))/nrow(df_filtered)*100, 2)
knitr::kable(round(table(data.frame(Time = cut(x, breaks = c(0, 10, 17, 24)), 
                       Weekday = df_filtered$Weekday))/nrow(df_filtered)*100, 2), 
             caption = "Repartition of the interactions for Weekdays and Time, in percentages of all the interactions")
```


### Summary

**Customers**  

In this cluster, there was `r nb_cust_all` customers, `r nrow(df_filtered)` interactions

**Travel time**  

| Interactions                          |Rest of the cluster|
|:-------------------------------------:|:-----------------:|
|   to go to the interaction (min)      |`r a_to_all`       |
|   from the interaction  (min)         |`r a_from_all`     |
|   total travelling time  (min)        | `r a_tot_all`     |

**AOV**    
- comarison of the AOV, on average, between the rejected interactions and all the cluster.

| Interactions                    |Rest of the cluster|
|:-------------------------------:|:-----------------:|
|   AOV                           | `r aov_all`       |

**Timeslots**  
- among the `r nrow(df_filtered)` rejected interactions, the repartition for the timeslots is the following:

| Interactions             |     Fractions (%)      |
|:------------------------:|:----------------------:|
|   before 10am (excl.)    | `r frac_timeslots[1]`  |
|   between 10am-6pm       | `r frac_timeslots[2]`  |
|   after 6pm (incl.)      | `r frac_timeslots[3]`  |

**Weekdays**  
- among the `r nrow(df_filtered)` rejected interactions, the repartition for the weekdays is the following:

| Interactions  |     Fractions (%)       |
|:-------------:|:-----------------------:|
|   Monday      | `r frac_weekday[1]`     |
|   Tuesday     | `r frac_weekday[2]`     |
|   Wednesday   | `r frac_weekday[3]`     |
|   Thursday    | `r frac_weekday[4]`     |
|   Friday      | `r frac_weekday[5]`     |
|   Saturday    | `r frac_weekday[6]`     |
|   Sunday      | `r frac_weekday[7]`     |











